\clearpage
\begin{centering}
\textbf{ACKNOWLEDGEMENTS}\\
\vspace{\baselineskip}
\end{centering}
Doing a part time degree is never easy. Doing a part-time PhD eight time zones away from campus while juggling a professional career and family should have been almost impossible. But it wasn't. That transformation from the abstract to the achievable was made possible by amazing advisors, Dr. Bahram Gharabaghi and Dr. Jesse Th\'e. Their support, encouragement and mentoring made these 3 years possible by arranging remote video classes to meet my course requirements, providing expert advise, recommending appropriate journals to submit to and occasionally providing a necessary kick in the backside.

The other members of my committee, Dr. Graham Taylor and Dr. Ed McBean, gave me the programming and statistical tools I needed to complete this program, as well as a new passion in machine learning and enjoyment in Python.

I am grateful beyond measure to the Natural Sciences and Engineering Research Council of Canada (NSERC), Mitacs, and Lakes Environmental for their funding and financial support and the University of Guelph's Department of Engineering for the flexible and kind support, especially when I let registration dates slip.

While much of the data used in this thesis was collected during a United Nations Development Program project, it would be ungrateful of me not to thank my colleagues (and friends) at the Kuwait Environment Public Authority, Department of Air Quality and Follow-Up for their assistance, especially Meshal Abdullah and Athari Al Aseed in the Stationary Sources office. I also want to thank my colleague Shah Faisal who worked with me during this UNDP project and who I still go back to for advice and technical questions on all things GIS.

For the UAS traffic data collection, my thanks go out to Dr Musaed Al Najat and Dr Jamal Ahmad from the Kuwait Traffic Safety Society for organizing flight approvals with the Ministry of Interior.

My parents, sister, and sons also played a collective part, even while located in another continent. They made things easier, especially during my trips back to North America, so I could focus on this research. 

My beautiful and loving partner, Manuela, provided a wonderful environment (and great food) to complete my work in- all while putting up with my late hours, self-absorbed studying, and random curses when my code did not work, with patience and understanding.

Lastly, some people may complete their studies without dogs, but I would not recommend it. My girls were always there and always ready to lift my spirits.

It's been a wonderful journey.





\clearpage
%\pagenumbering{gobble}  %remove page number on summary page




